SAT Competition 2020\tnoteref{title}

### 2020-11-24 paper/main.tex
abstract and small improvements

\begin{abstract}
We describe the 2020 SAT Competition and provide a detailed analysis of its results.
\end{abstract}

@@

\todo{Motivational paragraphs for SAT and the Competitions and what made this Competition Special}

@@

\todo{Present the structure of the paper}

\section{Overview: Descriptions of Tracks, List of Participants}

@@

This year in the Main Track, we had a Planning Sub-Track. 
The general idea is, that next to a balanced selection of benchmark instances in main track, to each year also offer one domain-specific sub-track.

%\newcommand{\stack}[2]{\begin{tabular}{@{}c@{}}#1 \\#2\end{tabular}}

@@

\begin{table}[h!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Variant & \bf Award \\
\hline

@@

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistChronoBT} & f2trc & \\
 & & f2trc-s & \thirdu\\
 \cline{2-4}
 & MapleLCMDistCBT-DL & f2trc & \\
\hline

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{ExMapleLCMDistChronoBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

@@

\begin{table}[h]
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Awards\\
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
 & P-MCOMSPS-STR-64 & \firsto \\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & Plingeling & \secondo \thirds \firstu \\
 & Treengeling & \\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & ManyGlucose-32 & \thirdo \thirdu \\
 & ManyGlucose-64 & \thirdu \\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & painlessmaplevone & \seconds \\
 & painlessmaplevtwo & \seconds \\
\hline
Li, Wu, Xu, Chen & syrupscavel & \\
\hline
Chen & abcdsatptwenty & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the parallel track.}
\end{table}

@@

\begin{table}[h]
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

\section{Selection and Maintenance of Benchmark Instances}

GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities\footnote{https://pypi.org/project/gbd-tools/} to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.\footnote{\url{https://gbd.iti.kit.edu}}

For selection of benchmarks in this competition, we used a database which contains information about instance author, family and result for a collection of instances used in all SAT competitive events dating back to 2006.\footnote{\url{https://gbd.iti.kit.edu/getdatabase/meta.db}} 
Like this it was possible to query for instances with desired properties, which gives the instance selection process a new quality. 
Using GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

@@

\section{Competition Results}
\todo{for each track summarize the descriptions of the winning solvers}

@@

\section{Analysis of Results}

@@

\section{Conclusion}

>>>>

\begin{abstract}
SAT Competition 2020 stands in the tradition of the series of annual competitive events which motivate and assess the progress in SAT solving. 
This competition was special as it introduced the new cloud track where SAT Solvers that run on hundreds of processors can compete. 
Another novelty is the application-specific sub-track of the main track, where solvers compete in solving benchmark instances from one specific domain only, and in this year that was the planning domain. 
We use new tools to select and distribute benchmark instances and their attributes. 
In this paper we provide a description of the well-known and the new competition tracks and how we organized them. 
It follows then a detailed analysis of the results and the strategies of the award winning solvers. 
\end{abstract}

@@

Propositional satisfiability (SAT) is the archetypal NP-complete problem. 
Despite its complexity, there is ongoing progress in solving methods and their implementations in SAT solvers. 
The generic nature of the SAT problem as well as the performance of state-of-the-art SAT solvers facilitate their use as the algorithmic backend in a plethora of applications. 
Today, SAT solvers are used for verification of hard- and software, product configuration, cryptography, planning and scheduling, to name a few. 
In mathematics, SAT solvers were recently even used to generate a record sized proof (200 TB) for an until then unsolved problem in Ramsey theory.

SAT Competitions are organized regularly since 1992 in order to drive progress and to serve as a public assessment of the state-of-the-art in SAT solving. 
For each SAT Competition, a set of new benchmark instances is compiled which reflects the various applications of interest to the community.

In this competition, we initiated a new application-specific subtrack. 
The idea is to provide a large amount of benchmark instances of a specific application, and to evaluate all solvers with respect to these instance in a special track. 
In this competition, we used 200 instances of the planning domain to run a planning subtrack.

Faster networks, distributed systems, and the increasing number of processors in modern computers show that the trend of increasing parallelism is about to continue.  
In the new cloud track, for the first time, solver authors could compete in SAT technologies that allow hundreds of SAT solvers to cooperate in solving a SAT instance.

@@

In Section~\ref{sec:tracks}, we start with a detailed description of the competition tracks and their purpose. 
Section~\ref{sec:instances} contains an overview on the selected benchmark instances and details about the selection process. 
In Section~\ref{sec:results}, we present the competition results alongside a survey on the winning strategies of the award winning solvers. 
A meta-analysis of these results follows in Section~\ref{sec:analysis}, and we conclude with Section~\ref{sec:conclusion}.

\section{Descriptions of Tracks}
\label{sec:tracks}

@@

@@

\begin{table}[h!]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|l|l|}
\hline
\bf Team & \bf Base Solver & \bf Variant & \bf Award \\
\hline

@@

\multirow{3}{*}{Kochemazov} & \multirow{2}{*}{MapleLCMDistCBT} & f2trc & \\
 & & f2trc-s & \thirdu\\
 \cline{2-4}
 & MapleLCMDistCBT-DL & f2trc & \\
\hline

@@

\multirow{4}{*}{\stack{Tchinda, }{Djamegni}}
 & \multirow{4}{*}{MapleLCMDistCBT} & padc\_dl & \\
 &  & padc\_dl\_ovau\_lin & \\
 &  & padc\_dl\_ovau\_exp & \\
 &  & psids\_dl & \\
% \cline{2-3}& Glucose 3.0 & upGlucose-3.0\_PADC\\
\hline

@@

\begin{table}[h]
\smaller
\arrayrulecolor{gray}
\centering
\begin{tabular}{|l|l|c|}
\hline
\bf Team & \bf Solver & \bf Score\\
\hline
\stack{Soos, Cai, Devriendt, }{Gocht, Shaw, Meel}~ & Cryptominisat-5 & 3 \\
\hline
\stack{Biere, Fazekas, }{Fleury, Heisinger}~ & Cadical-sc2020 & 1 \\
\hline
Chen & abcdsat-i20 & 1 \\
\hline
Manthey & Riss-7.1.2 & 1 \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the Incremental Library Track. Highest Score (=number of won categories) won the track.}
\end{table}

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Awards\\
\hline
\multirow{2}{*}{\stack{Vallade, Le Frioux, Baarir, }{Sopena, Kordon}}~
 & P-MCOMSPS-STR-32 & \firsto \firsts \secondu \\
 & P-MCOMSPS-STR-64 & \firsto \\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}
 & Plingeling & \secondo \thirds \firstu \\
 & Treengeling & \\
\hline
\multirow{2}{*}{Nabeshima, Inoue}
 & ManyGlucose-32 & \thirdo \thirdu \\
 & ManyGlucose-64 & \thirdu \\
\hline
\multirow{2}{*}{Tchinda, Djamegni}
 & painlessmaplevone & \seconds \\
 & painlessmaplevtwo & \seconds \\
\hline
Li, Wu, Xu, Chen & syrupscavel & \\
\hline
Chen & abcdsatptwenty & \\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the parallel track.}
\end{table}

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{|l|l|l|}
\hline
\bf Team & \bf Solver & \bf Rank\\
\hline
Schreiber & mallob-mono & 1\\
\hline
\stack{Ehlers, Kulczynski, }{Nowotka, Sieweck}~ & TopoSAT2 & 2\\
\hline
Riveros & Slime & 3\\
\hline
\multirow{2}{*}{\stack{Biere, Fazekas, }{Fleury, Heisinger}}~ & Paracooba & -\\
& Paracooba-March & -\\
\hline
Hartung & CTSat & -\\
\hline
\end{tabular}
\caption{Teams and Solvers participating in the cloud track.}
\end{table}

\section{Description of Benchmark Instances}
\label{sec:instances}

For selection of benchmark instances in this competition, we used GBD Tools\footnote{\url{https://pypi.org/project/gbd-tools/}}. 
GBD Tools is a tool-chain for maintenance and distribuation of benchmark instances and instances features~\cite{Iser:2018:GBD}. 
Its database\footnote{\url{https://gbd.iti.kit.edu}} contains information about all instances used in SAT competitive events dating back to 2006. 
In GBD Server, each instance also has an URL, such that instances can also be distributed by using their identifier: \url{https://gbd.iti.kit.edu/file/<gbd-hash>}.

Using the concept of instance identification via GBD Hash, which is the hash-sum of the unpacked and normalized DIMACS file, GBD Tools provide utilities to query for instances with specific properties, while maintaining the association of instance-id and instance attributes in publicly available databases.
Like this it is possible to query for instances with desired properties, e.g., instance author, family and result, which gives the instance selection process a new quality.

@@

\section{Competition Results}
\label{sec:results}
\todo{for each track summarize the descriptions of the winning solvers}

@@

\section{Analysis of Results}
\label{sec:analysis}

@@

\section{Conclusion and Prospects}
\label{sec:conclusion}
